### 2018-10-23 TeX/organigram1.tex
added database and stats field to TikX picture

	%% final result
	\node (testres) [res, right of = cas, xshift = 14cm, yshift = -5cm] {Result};
	\node (filtres) [res, right of = testres, xshift = 2cm] {Filter};
	\node (aggres) [res, right of = filtres, xshift = 2cm] {Aggregate};

	\begin{pgfonlayer}{bg3}
	\node[rectangle, draw, rounded corners, minimum height = 2cm, minimum width = 7cm, fill = gray!10, right of = testres, xshift = 1.5cm] (appbox) {};
	\end{pgfonlayer}

	\node (apptext) [above of = appbox, yshift = 0.25cm, xshift = -3cm] {Etox-Base Function};

@@

	\draw [arrow] (testres) -- (filtres); %++(2cm,0cm);
	\draw [arrow] (filtres) -- (aggres);

>>>>

	%% final result
	\node (testres) [res, right of = cas, xshift = 14cm, yshift = -5cm] {Result};

	% shiny
	\begin{pgfonlayer}{bg3}
	\node[rectangle, draw, rounded corners, minimum height = 2cm, minimum width = 7cm, fill = gray!10, right of = testres, xshift = 1.5cm, yshift = 4cm] (appbox_shiny) {};
	\end{pgfonlayer}
	\node (apptext) [above of = appbox_shiny, yshift = 0.5cm, xshift = -3cm] {Etox-Base Function};
	\node (filtres) [res, right of = appbox_shiny, xshift = -3.5cm] {Filter};
	\node (aggres) [res, right of = appbox_shiny, xshift = 0cm] {Aggregate};

	% database output
	\begin{pgfonlayer}{bg3}
	\node[rectangle, draw, rounded corners, minimum height = 2cm, minimum width = 7cm, fill = gray!10, right of = testres, xshift = 1.5cm, yshift = 0cm] (appbox_db) {};
	\end{pgfonlayer}
	\node (apptext) [above of = appbox_db, yshift = 0.5cm, xshift = -3cm] {Database output};
	\node (tableres) [res, right of = appbox_db, xshift = -2cm] {Postgres Table};
	% stats
	\node (stats) [res, below of = tableres, yshift = -2cm] {re\_stats.R};

@@

	% Result arrows
	\draw [arrow] (testres) -- (appbox_shiny.west); %++(2cm,0cm);
	\draw [arrow] (testres) -- (appbox_db.west);
